\section{Fundamentals}
\label{sec:fundamentals}
	
	\subsection{Soil Parameters}
	\label{ssec:soil-parameters}
	
		Let $A$ be any substance in a given soil sample with volume $V\in[0,\infty)$ and let $n_A\in[0,\infty)$ be the amount of $A$ in the sample.
		Then the molar concentration $c_A$ is given by
		\[
			c_A \define \frac{n_A}{V}
		\]
		Now let $c_0$ be the molar concentration of this sample.
		We define the amount-of-substance fraction (ASF) $p_A$ of $A$ as 
		\[
			p_A \define 100\%\cdot\frac{c_A}{c_0}
		\]

		In this elaboration we concentrate on three main soil parameters that are given by existing NIRS-measurements.
		The first two parameters $p_\m{SOC}$ and $p_\m{N}$ are ASFs relating to soil organic carbon (SOC) and nitrogen in the soil sample.
		SOC is the carbon in this sample which is bound in an organic compound.
		The third parameter is the $\m{pH}$-value that is used to specify the acidity or basicity of an aqueous solution.
		It is based on the concentration of hydronium ions $c_\m{H_3O^+}$.
		\[
			\m{pH} \define -\log_{10} c_\m{H_3O^+} = -\frac{\ln c_\m{H_3O^+}}{\ln 10}
		\]
	
	% subsection soil-parameters

	\subsection{NIRS}
	\label{ssec:nirs}
	
		In NIRS one uses electromagnetic waves, also known as light, with a wavelength from $780\unit{nm}$ to $3000\unit{nm}$.
		This area is called the near infrared region and is the most energetic one of the infrared light.
		% Quelle: https://de.wikipedia.org/wiki/Nahes_Infrarot

		An emitted light wave with a certain wavelength $\lambda$ can interact with a soil sample in three ways.
		It can be reflected, absorbed or transmitted.
		For most soil samples measuring the transmittance of light waves is not sensible.
		So the measurement of the spectrum is reduced to the reflectance since absorptance cannot be directly determined.
		
		

		Reflectance $\varrho(\lambda)$ of a surface referring to a wavelength $\lambda$ of a light wave is given by the amount of radiation power $P_\m{r}$ that is reflected from a surface divided by the initial power $P_0$ of this light wave.
		\[
			\varrho \define \frac{P_\m{r}}{P_0}
		\]
	
	% subsection nirs

% section fundamentals